Index measures for oak decline severity using phenotypic descriptors

### 2020-02-10 manuscript/manuscript.Rmd
moved discussion element from results to discussion
added word document template

---
output: 
  word_document: default
  pdf_document: default
fontsize: 12pt
header-includes:
  - \linespread{2}
  - \usepackage{lineno}
  - \linenumbers
bibliography: references.bib
---

@@

# Title: Index measures for oak decline severity using phenotypic descriptors {-}

>>>>

---
output: 
  word_document:
    reference_docx: template.docx
  pdf_document: default
fontsize: 12pt
header-includes:
  - \linespread{2}
  - \usepackage{lineno}
  - \linenumbers
bibliography: references.bib
---

@@

# **Title:** Index measures for oak decline severity using phenotypic descriptors {-}
